---
title: "eds221-interactive_sesionday7"
format: html
editor: visual
---

## Day 7 interactive session 

```{r}
library(tidyverse)
library(palmerpenguins)
library(lubridate)
library(ggplot2)
```

## **2. Data wrangling refresher**

**Refresher 1:** Starting with the `penguins` dataset in the `palmerpenguins` package, write a single piped sequence in which you:

1.  Only include penguins at Biscoe and Dream islands

2.  Remove the `year` and `sex` variables

3.  Add a new column called `body_mass_kg`, with penguin mass converted from grams to kilograms

4.  Rename the `island` variable to `location`

```{r}

penguins<- palmerpenguins::penguins


penguins_filter <- penguins %>% 
filter(island %in% c("Biscoe", "Dream")) %>% 
select(-year,-sex) %>% 
  mutate(body_mass_kg=body_mass_g *0.001) %>% 
  rename(location=island)





```

**Refresher 2:** Staring with the `penguins` dataset in the `palmerpenguins` package, write a single piped sequence in which you:

1.  Limit to only Adelie penguins

2.  Remove any observations where `flipper_length_mm` is `NA` (hint: `!is.na()`)

3.  Group the data by `sex`

4.  Find the mean (`mean()`), standard deviation (`sd`) and sample size (`n`) of flipper_length_mm for male and female Adelie penguins, returned in a nice summary table

```{r}
penguins_adelie <- penguins %>% filter(species %in% c("Adelie")) %>% filter(!is.na(flipper_length_mm)) %>%
  group_by(sex) %>% 
  summarise(mean = mean(flipper_length_mm, na.rm=TRUE), #to make one table summarizing all
  sd = sd(flipper_length_mm,na.rm=TRUE), 
  sample=n() #it counts the number of sample
  )

penguins_adelie2 <- penguins %>% filter(species == "Adelie") %>%
  filter(!is.na(flipper_length_mm)) %>%
  group_by(sex) %>%
  summarise(
    mean_flipper_length = mean(flipper_length_mm,na.rm=TRUE),
    sd_flipper_length = sd(flipper_length_mm,na.rm=TRUE),
    sample_size = n()
  )

penguins_adelie3 <- penguins %>% filter(species == "Adelie" & !is.na(flipper_length_mm)) %>%
  group_by(sex) %>%
  summarise(
    mean_flipper_length = mean(flipper_length_mm),
    sd_flipper_length = sd(flipper_length_mm),
    sample_size = n()
  )
```
